A survey of HTTP caching implementations on the open Semantic Web

### 2015-03-11 sanity/paper1.tex
Split HTTP into subsection
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@1049 43ef1190-90fd-4dd7-a769-d0121f02b80e

Caching may be deployed at several different levels: An HTTP cache may
be in a reverse proxy close to the server, in which case it may have
much in common with a conventional database cache. It may also be
anywhere between a server and a client, in which case it may be
shared, i.e. it may cache responses from several servers served to
several clients. Another example is an institutional forward proxy,
which are close to several users. Finally, the User Agent may
implement a private cache for its user at the client side.\todo{split here}

As mentioned, two standards are relevant for this study, RFC7234,
which is named ``Caching'' and RFC7232, named ``Conditional
Requests''. The main difference is that the caching standard defines
when a response may be reused without contacting the origin server at
all, whereas the conditional requests define how to validate a
response by contacting the origin server. The two can be combined:
Clients and proxies may use the latter to revalidate a response that
has been cached based on the former.

>>>>

Caching may be deployed at several different levels: An HTTP cache may
be in a reverse proxy close to the server, in which case it may have
much in common with a conventional database cache. It may also be
anywhere between a server and a client, in which case it may be
shared, i.e. it may cache responses from several servers served to
several clients. Another example is an institutional forward proxy,
which are close to several users. Finally, the User Agent may
implement a private cache for its user at the client side.

\subsection{HTTP Caching standards}

As mentioned, the two documents from the HTTP 1.1 standards suite that
are relevant for this study are RFC7234, which is named ``Caching''
and RFC7232, named ``Conditional Requests''. The main difference is
that the caching standard defines when a response may be reused
without contacting the origin server at all, whereas the conditional
requests define how to validate a response by contacting the origin
server. The two can be combined: Clients and proxies may use the
latter to revalidate a response that has been cached based on the
former.
